
    The 8 directions of the mask for the Gabor Wavelets
    
\textit{Haralick Features}

Haralick, a professor of the University of New York has realized an algorithm which allow to extract 14 features of an picture : 

\begin{itemize}
\item The angular second moment (ASM) which measure the local homogeneity of the picture.
\end{itemize}
\begin{itemize}
\item The contrast which analyze the image contrast between a pixel and its neighbor
\end{itemize}
\begin{itemize}
\item The correlation which analyze the linear dependency of grey levels of neighboring pixels.
\end{itemize}
\begin{itemize}
\item Compute the variance of the image
\end{itemize}
\begin{itemize}
\item Measure the gray tone variance
\end{itemize}
\begin{itemize}
\item Compute the inverse difference moment : relates inversely to the contrast measure
\end{itemize}
\begin{itemize}
\item The sum average, the entropy, sum entropy and difference entropy allow to analyses the randomness
\end{itemize}

\textit{Histogram oriented gradient (HOG)}

The Histogram oriented gradient is a tool to help classification, detection, and tracking. It encode
local shape information from regions or from point locations within an image.
This algorithm computes the zones regularly distributed in order to classify similar elements of a picture. 

\textit{Gray level co-occurrence matrix (GLCM)}

This algorithm extracts statistical texture features.
It detects four image characteristics:
\begin{itemize}
\item The contrast
\end{itemize}
\begin{itemize}
\item The correlation 
\end{itemize}
\begin{itemize}
\item The energy which measure the textural uniformity
\end{itemize}
\begin{itemize}
\item The homogeneity which is a uniform testing of an area of the picture
\end{itemize}

\textit{Segmentation-based Fractal Texture Analysis (SFTA )}

This algorithm which allows to create fractal image in order to detect the
roughness of an image. The fractal is the replication of a geometric form at every scale.
The roughness is a texture of a surface or edge that is not smooth but is irregular and uneven
    
\textit{Local Binary Pattern (LBP )}

The local binary patterns are the characteristics used to recognise the texture and the shape or to detect
objects into digital pictures. It compares the level of luminance of a pixel.
It's an algorithm which allows the calculation of the skewness and kurtosis.
The skewness is the computation of the lack of symmetry of a picture.
The kurtosis is the computation of the distribution of the gray level on a picture. If this value is positive,
the distribution of the gray level is uniform. If the kurtosis is negative, most of the color are a
medium intensity.

This algorithm select a group of 3x3 pixels, it compare the central pixel of this square, if the intensity of this pixel is higher or equal of his neighbourhood, this later get a value of 0, otherwise it obtain a value of 1.


    
    
    